Matching Bullets

### 2015-12-04 imaging-paper.Rnw
fig 14 and 15

\begin{figure}
\centering
    \begin{subfigure}[t]{\linewidth}
\caption{Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=bullet, size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey30", size=0.5) +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() +
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{Using a rolling median peaks and grooves are identified for each crosscut. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='\\textwidth', warning=FALSE>>=
  lof <- processBullets(paths = images[c(5,7)], x = 100)
  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

  b12 <- unique(lof$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 30)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 30)
  p1 <- peaks1$plot + xlab("y") + ylab("smoothed crosscut") + ggtitle(b12[1])
  p2 <- peaks2$plot + xlab("y") + ylab("smoothed crosscut") + ggtitle(b12[2])
grid.arrange(p1, p2, ncol=1)
@
}
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Rectangles in the back identify a line on one of the bullets.  Matching striation marks are indicated by color filled rectangles and arked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
<<smoothmatch, echo=FALSE, dependson='twolands100match', fig.width=7, fig.height=2.75, out.width='\\textwidth'>>=
peaks1$lines$bullet <- b12[1]
peaks2$lines$bullet <- b12[2]

@@

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6,  data = lines, alpha=0.2) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, colour=bullet)) +
  scale_colour_brewer("", palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
  theme(legend.position="none") +
  ylab(expression("Crosscut values in",mu,m)) +
  xlab("y")

# ggplot() +
#   geom_rect(aes(xmin = miny, xmax = maxy), ymin = 0.25, ymax=2.75, fill="grey80", data = subset(lines, lineid != 0)) +
#   geom_tile(data=lofX, aes(x=y, y=bullet, fill=type)) + 
#   scale_y_discrete(expand = c(0.2,0)) +
#   scale_fill_brewer(palette="Set2") + 
#   theme_bw() +
#   ylab("") +
#   theme(legend.position="bottom") +
#   geom_text(aes(x = meany), y= .4, label= "x", data = subset(lines, !match & lineid !=0)) +
#   geom_text(aes(x = meany), y= .4, label= "o", data = subset(lines, match & lineid !=0))
@
    }
\end{subfigure}
\caption{\label{fig:match} Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}

@@

reslist <- lapply(crosscuts[-1], function(cc) {
  b2 <- subset(lof, x %in% c(cc, 100))
  lofX <- bulletSmooth(b2)
  bAlign = bulletAlign(lofX)
  lofX <- bAlign$bullet  
  threshold <- bulletPickThreshold(lofX, thresholds = seq(0.3, 1.5, by = 0.05))

  lines <- striation_identify(lofX, threshold = threshold)
  maxCMS <- maxCMS(lines$match==TRUE)
  list(maxCMS = maxCMS, ccf = bAlign$ccf, threshold=threshold, lines=lines, bullets=lofX)
})

@@

lop <- lapply(reslist, function(res) {
ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=miny, xmax=maxy), ymin=-6, ymax=5, fill="grey90", data=res$lines) +
  geom_line(aes(x = y, y = l30, colour = bullet),  data = res$bullets) +
  geom_hline(yintercept = res$threshold) +
  geom_hline(yintercept = - res$threshold) +
  scale_colour_brewer("", palette="Set1") +
  theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match))
})

@@

reslist <- lapply(1:length(crosscuts[-1]), function(i) {
  b2 <- subset(lof, x %in% crosscuts[i:(i+1)])
  lofX <- bulletSmooth(b2)
  bAlign <- bulletAlign(lofX)
  lofX <- bAlign$bullet  
  threshold <- bulletPickThreshold(lofX, thresholds = seq(0.3, 1.5, by = 0.05))

  lines <- striation_identify(lofX, threshold = threshold)
  maxCMS <- maxCMS(lines$match==TRUE)
  list(maxCMS = maxCMS, threshold=threshold, ccf = bAlign$ccf, lines=lines, bullets=lofX)
})

>>>>

\begin{figure}
\centering
    \begin{subfigure}[t]{\linewidth}
\caption{Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=bullet, size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey30", size=0.5) +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() + ylab("Residuals of Loess Fit") + 
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{Using a rolling median peaks and grooves are identified for each crosscut. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='\\textwidth', warning=FALSE>>=
  lof <- processBullets(paths = images[c(5,7)], x = 100)
  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

  b12 <- unique(lof$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 30)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 30)

  library(RColorBrewer)
  col <- brewer.pal(3, "Set1")
  p1 <- ggplot() + theme_bw() +
    geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=6, data=peaks1$lines,  alpha=0.2) +
    geom_vline(aes(xintercept=extrema, colour=factor(type)), data= peaks1$lines) + scale_colour_brewer(palette="Set2") + 
    scale_fill_brewer(palette="Set2") +
    theme(legend.position="none") + 
    geom_line(aes(x=y, y=l30, group=bullet), data=subset(lofX, bullet==b12[1])) +
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
    ggtitle(b12[1])+ xlim(c(0, 2000))

  p2 <- ggplot() + theme_bw() +
    geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=6, data=peaks2$lines,  alpha=0.2) +
    geom_vline(aes(xintercept=extrema, colour=factor(type)), data= peaks2$lines) + scale_colour_brewer(palette="Set2") + 
    scale_fill_brewer(palette="Set2") +
    theme(legend.position="none") + 
    geom_line(aes(x=y, y=l30, group=bullet), data=subset(lofX, bullet==b12[2])) +
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
    ggtitle(b12[2]) + xlim(c(0, 2000))
grid.arrange(p1, p2, ncol=1)
@
}
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Rectangles in the back identify a line on one of the bullets.  Matching striation marks are indicated by color filled rectangles and arked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
<<smoothmatch, echo=FALSE, dependson='twolands100match', fig.width=7, fig.height=2.75, out.width='\\textwidth', warning=FALSE>>=
peaks1$lines$bullet <- b12[1]
peaks2$lines$bullet <- b12[2]

@@

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6.5,  data = lines, alpha=0.2, show.legend = FALSE) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6.5)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, colour=bullet)) +
  scale_colour_brewer("", palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
    theme(legend.position = c(1,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
  xlab("y")
@
    }
\end{subfigure}
\caption{\label{fig:match} Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}

@@

reslist <- lapply(crosscuts[-1], function(cc) {
#  browser()
  b2 <- subset(lof, x %in% c(cc, 100))
  lofX <- bulletSmooth(b2)
  bAlign = bulletAlign(lofX)
  lofX <- bAlign$bullet
    b12 <- unique(b2$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 35)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 35)

#  threshold <- bulletPickThreshold(lofX, thresholds = seq(0.3, 1.5, by = 0.05))
#  lines <- striation_identify(lofX, threshold = threshold)
  peaks1$lines$bullet <- b12[1]
  peaks2$lines$bullet <- b12[2]
  lines <- striation_identifyXXX(peaks1$lines, peaks2$lines)

  maxCMS <- maxCMS(lines$match==TRUE)
  list(maxCMS = maxCMS, ccf = bAlign$ccf, lines=lines, bullets=lofX)
})

@@

lop <- lapply(reslist, function(res) {
ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), show.legend=FALSE, ymin=-6, ymax=5, data=res$lines, alpha=0.2) +
  geom_line(aes(x = y, y = l30, colour = bullet),   data = res$bullets) +
  scale_colour_brewer("", palette="Set1", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match))
})

@@

reslist <- lapply(1:length(crosscuts[-1]), function(i) {
  b2 <- subset(lof, x %in% crosscuts[i:(i+1)])
  lofX <- bulletSmooth(b2)
  bAlign <- bulletAlign(lofX)
  lofX <- bAlign$bullet

  b12 <- unique(b2$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 35)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 35)

#  threshold <- bulletPickThreshold(lofX, thresholds = seq(0.3, 1.5, by = 0.05))
#  lines <- striation_identify(lofX, threshold = threshold)
  peaks1$lines$bullet <- b12[1]
  peaks2$lines$bullet <- b12[2]
  lines <- striation_identifyXXX(peaks1$lines, peaks2$lines)

  maxCMS <- maxCMS(lines$match==TRUE)
  list(maxCMS = maxCMS, ccf = bAlign$ccf, lines=lines, bullets=lofX)
})
